### 2023-04-17 README.Rmd
Update README, readme template for Apptainer/Singularity and FAQ with instructions in running containers

For running RStudio IDE in Apptainer/Singulairty container, some writable folders and a config file have to be created locally:

@@

After that, you can run the container (do not run as `root` user, otherwise you will not be able to login to RStudio IDE):

@@

or

```bash
singularity exec \
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf,.rstudio:/home/rstudio/.rstudio/ \
    container.sif \
    /usr/lib/rstudio-server/bin/rserver \
    --auth-none=0 --auth-pam-helper-path=pam-helper \
    --server-user=$(whoami) --www-port=8787
```

Now open a browser and go to localhost:8787.
The default username is your local username, password as specified above (in this case `set_your_password`).

>>>>

To run RStudio IDE in Apptainer/Singularity container, some writeable folders and a config file have to be created locally:

@@

After that, you can run the container (do not run as `root` user, otherwise you will not be able to login to RStudio IDE).

Start instance (on default RSTUDIO port 8787):

```bash
apptainer instance start \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf,.rstudio:/home/rstudio/.rstudio/ \
    container.sif \
    rangtest
```

Now open a browser and go to localhost:8787.
The default username is your local username, default password is 'set_your_password' (if you are using container generated by rang).

List running instances:

```bash
apptainer instance list
```

Stop instance:

```bash
apptainer instance stop rangtest
```

Start instance with custom port (e.g. 8080) and password:

```bash
apptainer instance start \
    --enc RPORT=8080
    --env PASSWORD='set_your_password' \
    --bind run:/run,var-lib-rstudio-server:/var/lib/rstudio-server,database.conf:/etc/rstudio/database.conf,.rstudio:/home/rstudio/.rstudio/ \
    container.sif \
    rangtest
```

Run container with custom `rserver` command line:

@@

If you run the container using `apptainer exec` command, you will have to kill the `rserver` process manually or Cmd/Ctrl+C from the running container to stop the server.
